SunPy - Python for Solar Physics

### 2014-01-28 2-Data_Types.tex
Note in the file on 2-data-types to say that the LightCurve object does not have a meta attribute

\section{Core Data Types}
The primary focus of SunPy is to provide data structures 
that are specifically designed for the various kinds of solar physics data, namely
images, time series, and spectra. SunPy provides three core data
types using Python classes:
\texttt{Map} (2D spatial data),
\texttt{LightCurve} (1D temporal series)
and \texttt{Spectrum}/\texttt{Spectrogram} (1 and 2D spectra).

The classes provide access to the original data
along with associated metadata and provide appropriate convenience functions to
enable data analysis and visualization. For each of these classes, the data is
stored in the \texttt{.data} attribute while the metadata is stored 
in the \texttt{.meta} attribute. It is 
possible to instantiate the data types from various different 
sources: \textit{e.g.}, files, URLs, arrays or time ranges.  In order to provide
instrument-specific specialisation, all the core SunPy data types support specialisation;
\textit{e.g.}, \texttt{Map} has an \texttt{AIAMap} sub-type. 
Data visualisation is provided by two functions: \texttt{peek()}, for quick plotting,
and \texttt{plot()}, for more fine-grained control plotting that integrates with 
\texttt{matplotlib}.

>>>>

\section{Core Data Types}
The primary focus of SunPy is to provide data structures 
that are specifically designed for the primary varieties of solar physics data, namely
images, time series, and spectra. SunPy provides three core data
types using Python classes:
\texttt{Map} (2D spatial data),
\texttt{LightCurve} (1D temporal series)
and \texttt{Spectrum}/\texttt{Spectrogram} (1 and 2D spectra).

The classes provide access to the original data
along with associated metadata and provide appropriate convenience functions to
enable data analysis and visualization. For each of these classes, the data is
stored in the \texttt{.data} attribute while the metadata is stored 
in the \texttt{.meta} attribute. It is 
possible to instantiate the data types from various different 
sources: \textit{e.g.}, files, URLs, arrays or time ranges.  In order to provide
instrument-specific specialisation, all the core SunPy data types support specialisation;
\textit{e.g.}, \texttt{Map} has an \texttt{AIAMap} sub-type. 
Data visualisation is provided by two functions: \texttt{peek()}, for quick plotting,
and \texttt{plot()}, for more fine-grained control plotting that integrates with 
\texttt{matplotlib}.
% LightCurve does NOT have a meta attribute.  It looks like this would
% be a simple fix in the main lightcurve class.
